\documentclass[blue]{beamer}
\usepackage{beamerthemeFrankfurt} 
\usecolortheme{rose}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{cite} % never use with beamer 
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage[most]{tcolorbox}
\usepackage{adjustbox}
\makeatletter
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\makeatother
\usepackage{url}
\newtheorem{assumption}{Assumption}
\usepackage{setspace}
\setbeamertemplate{itemize/enumerate body begin}{\small}
\usepackage{tabulary}
\usepackage[algo2e,linesnumbered,ruled,vlined]{algorithm2e} 
\makeatletter
\let\@@magyar@captionfix\relax
\makeatother
%\usepackage{algpseudocode,algorithm,algorithmicx}
\setbeamercolor{title}{fg=red!80!black,bg=red!20!white}

\usefonttheme{professionalfonts} % font theme
\newtheorem{answeredquestions}[theorem]{Answered Questions}
\usepackage[figuresright]{rotating}
\usepackage{subfig}
\graphicspath{{images/}{use/}{infersent/}}
%\usefonttheme[onlysmall]{structurebold} %%%small fonts in the navigation bars are a bit hard

\title{Research Presentation}
\author[Chandresh]{Chandresh Kumar Maurya \\ Research Assistant Professor\\ }
\institute{E\"otv\"os Lor\'and University, Budapest, Hungary}
\begin{document}
\maketitle
% without [fragile], any {verbatim} code gets mysterious errors.

\begin{frame}{About Me}

{\bf March 2019-}: Research assisstant professor at ELTE University, Budapest Hungary.\\
{\bf 2017-2019}:  Research Scientist at IBM Research at Bangalore\\
{\bf 2013-2016}:  Ph.D. student in Computer Science at IIT Roorkee, India. \\
{\bf 2010-2012}: M.Tech at JNU New Delhi, India\\
{\bf 2006-2010}: B.Tech at BIET Jhansi, India\\
\end{frame}

\begin{frame}
\frametitle{Outline}
  \tableofcontents %[pausesections]
\end{frame}


\section{Research Contribution}

\begin{frame}
\frametitle{Research Contribution}
My research area primarily has been in data mining and machine learning during Ph.D.  In the last two years, I have been working in the NLP, IR and IE domain. 
So far, I have worked on the following problems:
\begin{itemize}
\item Anomaly Detection in Big Data (Ph.D. Topic) ({\bf ML, DM, Convex optimization})
\item Creative Tagline Generation for Product Advertisement (under IBM"s CFP entitled "Creative AI") ({\bf ML, DM, NLP, IE})
\item Prediction of Invoice Payment Status in Account Payable Business Process. (Client project) ({\bf ML })
\item Similarity Learning with Feedback for Invoice Line Item Matching (Client Project) ({\bf  ML, NLP})
\item  Automatic extraction of change configuration requests from email tickets (Current work with T-labs and TU Berlin) ({\bf NLP via DL, IE})
\end{itemize}


\end{frame}

\begin{frame}
\footnotesize
\frametitle{Publications (Journals)}

\begin{enumerate} 
\item 

C. Maurya; D. Toshniwal; G. Venkoparao, ``Distributed Sparse Class-Imbalance Learning and its Applications," in {\bf IEEE Transactions on Big Data} , vol.PP, no.99, pp.1-1
https://doi.org/10.1109/TBDATA.2017.2688372

\item
Chandresh Kumar Maurya, Durga Toshniwal, Gopalan Vijendran Venkoparao, Online sparse class imbalance learning on big data, {\bf Neurocomputing}, Volume 216, 5 December 2016, Pages 250-260, ISSN 0925-2312, http://doi.org/10.1016/j.neucom.2016.07.040. (IF 3.317)

\item 
Chandresh Kumar Maurya, Durga Toshniwal, Large-Scale Distributed Sparse Class-Imbalance Learning with Application to Anomaly Detection,  {\bf Information Sciences}, Volume 456, 4 May 2018, Pages 1-12, ISSN 0020-0255, Elsevier, https://doi.org/10.1016/j.ins.2018.05.004 (IF 4.832)


\end{enumerate}
\end{frame}

\begin{frame}
\begin{enumerate} 


\item   Creative Tagline Generation Framework for Product Advertisement, Chandresh Kumar Maurya et al.,  in {\bf IBM Journal of Research \& Development}) (SCIE IF 0.6)
\item  Online Similarity Learning with Feedback for Invoice Line Item Matching (submitted to IEEE TKDE, short version accepted in {\bf AAAI 2020} workshop on intelligent process mining, NY, USA)
\item DeLAEE: A Deep Learning Architecture for Automated Essay Evaluation (under review in Neural Netowrks and Learning Systems,Springer)
\item Gmean optimization using PSO for Multi-Class Imbalance learning (under review in Applied Soft Computing)
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Publications (Conferences/Workshops)}

\begin{enumerate} 
\item 
Prediction of Invoice Payment Status in Account Payable Business Process. Tarun Tater, Sampath Dechu, Senthil Mani, and Chandresh Kumar Maurya, {\bf International Conference on Service-Oriented Computing (ICSOC)} 2018, China.

\item
 Anomaly Detection via Distributed Sparse Class-Imbalance Learning. Chandresh Kumar Maurya, Durga Toshniwal, and  Vishal Agarwal, ( presented in \textcolor{red}{International Conference on Machine Learning, ICML 2016} workshop on Anomaly detection, NY, USA)


\item
Online Anomaly Detection via Class-Imbalance Learning, Chandresh Kumar Maurya and Durga Toshniwal,  in  {\bf International Conference on Contemporary Computing (IC3)} , organised jointly by JIIT Noida and University of Florida, USA, Sep 2015.

\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Publications (Conferences/Workshops)}

\begin{enumerate} 


\item
 Anomaly Detection in Nuclear Power Plant Data using Support Vector Data Description, Chandresh Kumar Maurya and Durga Toshniwal, in  IEEE TechSym at IIT Kharagpur, Feb 2014.

\item  Fuzzy Inference System for Internet Traffic Load Forecasting, Chandresh Kumar Maurya and Sonajharia Minz. In the Proceedings of National Conference of Computing \& Communications (NCCCS)-
2012. DOI:10.1109/NCCCS.2012.6413010. .

\item
Anomaly Detection in Streaming Data using Online Non-negative Matrix Factorization, Chandresh Kumar Maurya, Arun Chauhan and Durga Toshniwal, poster presentation at International workshop on machine learning \& Text analytic(MLTA 2013), South Asian University, New Delhi.  (\textcolor{red}{Best  presentation Award})
\end{enumerate}
\end{frame}




\begin{frame}[shrink=20]
\footnotesize
\frametitle{Patents While @IBM}

\begin{enumerate} 
\item A System and Method for Automatic Adjustment of Brightness of Mobile Devices based on Visual Sight ({\bf  FILED})

\item A System and Method for Recommending Popular Features for a Product based on Crowd-source Reviews of the Product and Competitor Product  ({\bf Rated search-2 by IBM, under search}) 


\item A System and Method for Finding Best Accommodation using Deep Asthetic Features in Multimodal Data from Social Networks. ({\bf Defensive publication})

\item A System and Method for Automatic  Compliance Checking in Clinical Process using Deep Multi-task Learning. ({\bf  Defensive publication})

\item A system and Method for Similarity Learning with Heterogeneous Catalogues and Taxonomies for Invoice and PO Line Item Matching (under review).
\item  An Intelligent and Proactive Reminder System using Multi-Modal Data through AI (under review).

\item 
A System and Method for Consistency Verification of Product’s Information on E-commerce Portals (under review).
\end{enumerate}
\end{frame}


\begin{frame}{Projects}

\begin{itemize}
\item {\bf Evaluation of Effectiveness of Gerson Therapy for Cancer} (In collaboration with IIT Patna India and NTU Singapore, submitted for funding)

\item  {\bf Intelligent reminder system based on multi-model data} (Independent research)
\item  {\bf Multimodal incident similarity inference for improving ticket resolution}
(In collaboration with IBM Research and IIIT Gwalior, India)
\item {\bf  Feature/Suggestion recommendation based on crowd-source data}
(In collaboration with NIT Shilong, India, IBM Research and NTNU Norway)

\end{itemize}
\end{frame}

\begin{frame}{Extra-curricular}

\begin{tcolorbox}
\textsc{Project-guidance}
\end{tcolorbox}

\begin{itemize}
\item Currently, guiding one B.Tech student  at IIIT Gwalior (In collaboration with IBM Research)
\item Guiding 2 B.Tech students at NIT Shilong  (In collaboration with  IBM Research and NTNU Norway)
\item  Guided one  IDD students at IIIT-M Gwalior India for  dissertation 
\item Guided two M.Sc. students for their curriculum's projects at Eotvos Lorand University, Budapest, Hungary. 

\end{itemize}
\end{frame}

\begin{frame}{Extra-curricular}

\begin{tcolorbox}
\textsc{Invited Talks}
\end{tcolorbox}
\begin{itemize}
\item Invited talk at machine learning workshop at NIT Shilong, India Nov 1, 2018.
\item Invited as a resource person  for faculty development program at Visvesvaraya Technological University, Belgaon, India betwen dec 10-14, 2018.
\item Invited talk at Jawaharlal Nehru University, New Delhi, between Nov 7-9, 2016.
\end{itemize}

\end{frame}

\begin{frame}
\begin{tcolorbox}
\textsc{Scholorships/Awards}
\end{tcolorbox}

\begin{itemize}
\item Prime Minister Fellowship for Doctoral Research, awarded by Confederation of Indian Industry(CII, part of DST, Govt. of India New Delhi) and Robert Bosch Engineering \& Business Solution Ltd.(RBEI), Bangalore.
\item Awarded Topper's scholorship in the $1^{st}$  year of Undergradute.
\item Junior Research Fellowship by IIT Roorkee, INDIA.
\item Junior Research Fellowship by University Grant Commission, INDIA.
\end{itemize}

\end{frame}




\section{Future Research Plan}

\begin{frame}{Future research plans}
 My future research plans include the following:
 \begin{enumerate}
     \item External knowledge injestion in deep architectures
     \item Class-imbalance learning in multi-modal streaming data
     \item AI for social good
 \end{enumerate}
\end{frame}

%====================================================



%\section{Teaching plan}
%
%\begin{frame}{Teaching plan}
%Some of the basic and advanced subjects I would like to teach are:
%\begin{itemize}
%\item Design and analysis of algorithms
%\item Data Structures
%\item Linear algebra
%\item Probability \& Statistics
%\item Matrix Calculus
%
%\end{itemize}
%Advanced courses
%\begin{itemize}
%\item Machine Learning/Data Science
%\item Reinforcement learning
%\item Convex/non-convex optimization
%\item General AI
%\item NLP
%\item IR
%
%\end{itemize}
%
%\end{frame}



\begin{frame}[allowframebreaks]{Bibliography}
\fontsize{8pt}{7.2}\selectfont
\bibliographystyle{apalike}
\bibliography{./TKDE}
\end{frame}
\end{document}